
Finally, our project is about creating an Artificial Intelligence able to beat an human playing the Arimaa game.
\newline
\newline
Arimaa is a two players game. It has been designed to be difficult to foresee for computers, but easy to play for humans. 
In order to realize our project, we will need some concepts and technologies. 
We will use the MonteCarlo Tree Research algorithm, to take the best decisions in our game. We will decide what move to play according to this algorithm figures. Because of the numerous moves possible, we will need to choose to develop the better ones, that will depend on the chosen parallelization tree. Any variation could totally change statistics.
We already analyse the state of the art of Arimaa and the MonteCarlo Tree Research. Consequently, we will base our work on these thesis, to make it possible to use the best technologies with the best environment without doing what has already been done.
We already know how to play this game. So it would be easier to create strategies for our Artificial Intelligence. We handle a task's schedule to control our requirements. We will be able to give back our work to the due time. The point of this part is mostly to learn to schedule a project, foreseeing surprising events, and answering the demand.
\newline
\newline
The point of this project is as well to test our program upon Grid5000, a powerful network of multi-core machines. Then, we will use the entire potential of our program in his maximal capacities, against a human.
