One of the purposes of this project is to learn how manage and plan our work. For this we have to use MS Project to indicate all the tasks we have to do, who does each one, and how long it will be.  So how did we chose to do this ?
\newline
\newline
At the start of the project we added on MS Project all the deadlines that are demanding by the bill of the project. This deadlines are the differents reports (analysis, specifications, ..), the orals and the rendering of the code of the project. After this, each week we decide all tasks we will do for next week, then we add them on the planning and associated each one with the personn who will do it.
\newline
\newline
For the moment we don't plan the coding part because until we will have chose all the technologies we will use, there are many tasks that we can't estimate the length. The only one we do is to create a model of the game and its graphical interface to allow us to play the game. This will permit us to better understand the game and make easier the implementation of the artificial intelligence.
\newline
\newline
The second part plan is the UML modeling, during the preparation of the next report we will dedicate one week to it, with the specifications that we will define it will allow us to plan almost completely the coding of our project.
\newline
\newline

Another important point is the role distribution, for the moment we have define 3 specifics roles : 
\begin{itemize}
\item  Dan is the secretary. It means he has to organise the meetings and write their reports.
\item Gabriel is the master application, he has to the final decision about each point of the coding part.
\item Baptiste is in charge of the planning, it's him who sets the deadlines of every tasks, and who check that everything is doing in time.
\end{itemize}
Moreover each people is archivist, all of us have to search the informations that we need to realize our software. Those who don't have a special role for the moment will be responsible of one of the next reports.