\subsubsection{Human Resources}

Our project group is composed of six students, half of which will be abroad next semester.
That implies that most of the development phase will be carried out by a team of three people, with the help of the supervisors.
The planning has been done assuming that we would not recieve help from people outside the project, but we plan to ask Mr Garcia, a researcher from INSA, for advice.
Since he knows a lot about Artificial Intelligence, his help would help speed up the project.

\subsubsection{Other resources}

The algorithm is due to exploit parallelization in order to give more accurate results. We will first test it on the machines from INSA's Computer Science department;
then, if we have the time and the authorization required, we will run it on \emph{Grid'5000}, a set of clusters of multi-core machines.

\subsubsection{Exterior knowledge}

The Artificial Intelligence (\emph{AI}) will implement the \emph{Monte Carlo Tree Search} (\emph{MCTS}) algorithm, that has been used in the past for board games.
The AI will be parallelized using the \emph{Root parallelization} strategy, one of the main strategies used with the MCTS algorithm.

\subsubsection{Technologies used}

A few technologies will be used for this project:
\begin{itemize}
	\item The project will be coded using the C++ language
	\item The application providing a user interface uses SFML 1.6
	\item Either MPI, OpenMP and OpenACC or an implemntation of the actor model (such as \emph{CAF}) will be used for parallelization
\end{itemize}

\subsubsection{Important dates}

For this project, a number of set deadlines exist:
\begin{itemize}
	\item A conception report is due by the 12$^{th}$  of February
	\item A HTML documentation is due by the 25$^{th}$ of March
	\item The final report  is due by the 26$^{th}$ of May
	\item A demonstration of the AI will take place on the 26$^{th}$ of May
	\item The application is to be finished and sent by the 28$^{th}$ of May
	\item A presentation of the project will take place on the 28$^{th}$ of May
\end{itemize}

In order to give us more time to work on the project, some time has been freed on our schedule, from May the 18$^{th}$ to May the 28$^{th}$.
On the other hand, the exams that take place on the weeks of January the 12$^{th}$ and May the 11$^{th}$ have been considered as time off the project. 
Outside of these time periods, the workload for each member of the team has been set to 4 hours a week, in order to increase our flexibility.